Towards Globally Color-Dual All-Loop Integrands

### 2023-08-15 notes/2loopNLSM.tex
Added a gitignore to the notes.  Starting on the YM discussion.

@@

\subsection{Double-copy -- Alex }
\subsection{YM revisit -- Alex}

>>>>

%Comment commands
\newcommand{\ace}[1]{\textcolor{darkgreen}{\textbf{AE:}{#1}}}

@@

\subsection{Double-copy -- Alex }

\begin{itemize}
\item  ``Most important'' check of Jacobi -- imposes ``diff'' invariance in the DC numerators
\item Match against cuts from \cite{Carrasco:2023qgz}: double copy
  with N=0 \cite{Bern:2015ooa}, N=4, itself
  \item Whip up a non-jacobi N=0 or $\pi$ to highlight double copy success?
\end{itemize}

\subsection{YM revisit -- Alex}
Transition paragraph.....

As part of attemtping to construct a color-kinematics dual
representation for $\mathcal{N}=0$ Yang--Mills at two loops, Bern,
Davies, and Nohle (BDN) lay out the following core assumptions for
integrand numerators (in addition to obeying some form of the
kinematic Jacobi relations) \cite{Bern:2015ooa}
\begin{enumerate}
\item Locality: Diagram ``numerators'' are polynomials in momenta and
  polarizations, \eg the diagrams only have poles given by the
  propagators of the diagrams. \emph{We explore a minor breaking of this assumption}
\item Power-counting: The maximum power of the loop momenta in the
  numerator is boudned by Feynman-gauge Feynman rules.  \emph{We
    explore breaking this assumption}.
\item Cubic diagrams: The only diagrams with nonzero numerators are
  those with strictly cubic vertices.  This is generally a requirement
  to properly define the kinematic Jacobi relations.
\item Relabeling : The diagram numerators are only a function of the
  diagram's topology and labeling
\item Symmetries: The diagram numerators are invariant under the
  automorphisms of the diagrams \emph{including signs that compensate
    for color-factor sign changes}
\item Unitarity cuts: The cuts of the ansatz must reproduce the
  physical unitarity cuts of the theory.
\end{enumerate}
They demonstrated that the above assumptions are incompatible with an
off-shell solution to the kinematic Jacobi relations.  Here, we
explore two violations of these core assumptions.

First, we analyze the power-counting assumption.  In our labeling of
the two loop Jacobi-basis diagrams, shown in \ace{Figure out fig}, we
find that the power counting bound proposed by Bern, Davies, and Nohle
leads to an initial ansatz with XX terms in the double-box, and YY
terms for the penta-triangle.  However, recent work by Ben-Shahar,
Garozzo, and Johansson \cite{Ben-Shahar:2022ixa} \ace{Are there other
  good examples?} demonstrates that constructing Feynman rules that
produce manifestly color-dual numerators for the NMHV sector of
Yang--Mills requires introducing additional auxiliary fields,
including higher-spin modes, which could shift the expected power
counting in non-trivial ways.  We therefore attempt to find an
off-shell color-dual Yang--Mills representation in which all power
counting restrictions are lifted.

Without power counting restrictions, both the double-box and the
penta-triangle ansatz have an initial ansatz with 10,010 terms each.
Imposing diagram automorphisms on the two basis diagrams, we reduce
the number of terms to XX.  Gauge invariance on support of the maximal
cuts of the basis diagrams further reduces the remaining freedom to
YY.  The power-counting restriction of BDN would reduce this count to
ZZ.  In the original BDN work, they imposed three spanning generalized
unitarity cuts, shown in [].  Instead of directly imposing the
spanning cuts, we proceed with the relaxed version of the method of
maximal cuts used above in the pion construction [\ace{is James going
  to talk about something along this line in the pions section?}].  We
find that even with the completely generic ansatz, the representation
fails to satisfy the next-to-next-to-maximal cut shown in [].
Notably, imposing the BDN power-counting constraints additionally
causes a discrepancy with the N$^2$-max cuts show in [].

\begin{itemize}
\item Recap assumptions of \cite{Bern:2015ooa}
\item Going beyond ``Feynman-type counting'' $\to$ 10010 initial
  ansatz.  Compare post-(sym+GI) on BCJ basis.
\item Discuss which cuts still fail.  Double check these statements
  \item Attempt at non-local.  Still have problems with cuts+syms+jacobi
\end{itemize}
